---
title: "Exercicios_duas_variaveis"
author: "vinicius"
date: "5 de março de 2018"
output: html_document
---
***

### Carregar configurações e dataset
Notes:

```{r Scatterplots}

library(ggplot2)
data(diamonds)
?diamonds
```


***

### Histogramas de Preço com Facetas e Cor
Notes:

```{r Scatterplots}
diamonds$price

ggplot(aes(x = log(price), fill = cut), data = diamonds) +
  geom_histogram() +
  scale_fill_brewer(type = 'qual') +
  facet_wrap(~ color) +
  coord_cartesian(ylim = c(0, 600)) 

```


***

### Preço vs. Tabela Colorida por Corte
Notes:

```{r Scatterplots}

ggplot(aes(x= table, y = price), data = diamonds) +
  geom_point(aes(color = cut))+
scale_color_brewer(type = 'qual')+
scale_x_continuous(limits=c(50,80),breaks = seq(50,80,2))

```


***

### Tabela Típica de Valor
Notes:

```{r Scatterplots}
tapply(diamonds$table, diamonds$cut, summary)

```

***

### Preço vs. Volume e Claridade do Diamante
Notes: 
 Create a scatterplot of diamond price vs.
 volume (x * y * z) and color the points by
 the clarity of diamonds. Use scale on the y-axis
 to take the log10 of price. You should also
 omit the top 1% of diamond volumes from the plot.

 Note: Volume is a very rough approximation of
 a diamond's actual volume.

 The plot should look something like this.
 http://i.imgur.com/excUpea.jpg

 Note: In the link, a color palette of type
 'div' was used to color the scatterplot using
 scale_color_brewer(type = 'div')

```{r Scatterplots}
diamonds$volume <- (diamonds$x * diamonds$y * diamonds$z)
diamond_99_volume <- subset(diamonds, volume < quantile(diamonds$volume, c(0, 0.99)) & diamonds$volume != 0)

ggplot(aes(x= volume, y = price), data = diamond_99_volume) +
  geom_point(aes(color = clarity) ) +
  scale_y_log10()  +
  scale_color_brewer(type = 'div') +
  ggsave('volumeClarity.png')

#ou

ggplot(aes(x=volume, y=price), data= subset(diamonds, volume != 0)) +
  geom_point(aes(color=clarity)) +
  scale_y_log10() +
  xlim(0,quantile(diamonds$volume,.99)) + #x limit de 0 até 99% dos volumes
  scale_color_brewer(type = 'div') +
  ggsave('volumeClarity.png')
  

```

***

### Proporção de Amizades Iniciadas
Notes:

Many interesting variables are derived from two or more others.
For example, we might wonder how much of a person's network on
a service like Facebook the user actively initiated. Two users
with the same degree (or number of friends) might be very
different if one initiated most of those connections on the
service, while the other initiated very few. So it could be
useful to consider this proportion of existing friendships that
the user initiated. This might be a good predictor of how active
a user is compared with their peers, or other traits, such as
personality (i.e., is this person an extrovert?).

Your task is to create a new variable called 'prop_initiated'
in the Pseudo-Facebook data set. The variable should contain
the proportion of friendships that the user initiated.

```{r Scatterplots}
pf <- read.csv('pseudo_facebook.tsv', sep = '\t')

pf$prop_initiated <- pf$friendships_initiated/pf$friend_count

subset(pf, !is.na(pf$prop_initiated))


```


***

### prop_initiated vs. tenure
Notes:
Create a line graph of the median proportion of
friendships initiated ('prop_initiated') vs.
tenure and color the line segment by
year_joined.bucket.

Recall, we created year_joined.bucket in Lesson 5
by first creating year_joined from the variable tenure.
Then, we used the cut function on year_joined to create
four bins or cohorts of users.

(2004, 2009]
(2009, 2011]
(2011, 2012]
(2012, 2014]

The plot should look something like this.
http://i.imgur.com/vNjPtDh.jpg
OR this
http://i.imgur.com/IBN1ufQ.jpg



```{r Scatterplots}

#cria a variável year_joined tendo como ano base 2014
pf$year_joined <- floor(2014 - pf$tenure/365)
#cria os buckets dos períodos escolhidos
pf$year_joined.bucket <- cut(pf$year_joined,  c(2004, 2009, 2011, 2012, 2014))

ggplot(aes(x = tenure,  y = prop_initiated), 
       data = subset(pf, !is.na(year_joined.bucket))) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary', fun.y = median) +
  ggsave('prop_InitiatesByTenure.png')

```


***

### prop_initiated vs. tenure Smooth
Notes:
Smooth the last plot you created of
of prop_initiated vs tenure colored by
year_joined.bucket. You can bin together ranges
of tenure or add a smoother to the plot.

There won't be a solution image for this exercise.
You will answer some questions about your plot in
the next two exercises.

Resposta: -0.0106474

```{r Scatterplots}

ggplot(aes(x = tenure,  y = prop_initiated), 
       data = subset(pf, !is.na(year_joined.bucket))) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary', fun.y = median) +
  geom_smooth() +
  ggsave('prop_InitiatesByTenureSmooth.png')


```

***

### The best group prop_initiated
Notes: On average, which  group initiated the greatest proportion of its Facebook friendships? The plot with the smoother that you created in the last exercise can help you answer this question.

Resposta: People who joined after 2012


***

### Largest Group Mean prop_initiated
Notes:For the group with the largest proportion of friendships initiated, what is the group's average (mean) proportion of friendships initiated?.

Resposta: 0.6654

Why do you think this group's proportion of friendships initiated is higher than the others?

Resposta: Acredito que não exista somente uma resposta, mas uma das possíveis, é que hoje o facebook está bem consolidado e as pessoas mais novas encontram com mais facilidade seus amigos.

```{r Scatterplots}

summary(subset(pf$prop_initiated, pf$year_joined > 2012))
```


***

### Price/Carat Binned, Faceted e Colored
Notes:
Create a scatter plot of the price/carat ratio
of diamonds. The variable x should be
assigned to cut. The points should be colored
by diamond color, and the plot should be
faceted by clarity.

The plot should look something like this.
http://i.imgur.com/YzbWkHT.jpg.

Note: In the link, a color palette of type
'div' was used to color the histogram using
scale_color_brewer(type = 'div')


Observação: 
@Sheng_Kung
"When we have data that falls into categories, scatterplots can be difficult to interpret due to overplotting on the individual levels of that feature. What we can do to alleviate this and make the plot easier to read is to use positional jittering. Take a look at http://ggplot2.tidyverse.org/reference/position_jitter.html of the documentation for some examples of use of the position_jitter function.

When we jitter the points in the plot horizontally, this allows us to better see what the distribution of points are within each level, especially since we have a multivariate plot where we are coloring points by diamond color grade. It's much easier to see how the color grades are distributed when the points are jittered. Functionally, we should not think of points that are off-center as being any different from points close-to-center in each group. The data should still be interpreted as categorical as before. One thing to keep in mind is that you should have a gap between columns of data so that it is clear to which level each point belongs - without a gap, category inclusion becomes difficult to discern. So make sure you pay attention to the width and height parameters when using position_jitter so that you can still interpret the plot properly."

```{r Scatterplots}

ggplot(aes(x = cut, y = price/carat),
       data = diamonds) +
  geom_jitter(aes(color=color), position = position_jitter(width = 0.4, height = 0.4)) +
  facet_wrap(~ clarity) + 
  scale_color_brewer(type = 'div') +
  ggsave(file='pricePerCaratFaceted.png', width = 11, height = 11 ,dpi = 300)


```



