Lesson 5
========================================================

### Multivariate Data
Notes:

***

### Moira Perceived Audience Size Colored by Age
Notes:

***

### Third Qualitative Variable
Notes:

```{r Third Qualitative Variable}
library(ggplot2)
pf <- read.csv('pseudo_facebook.tsv', sep = '\t')

#stat_summary indica onde está a média no box plot
ggplot(aes(x = gender, y = age),
       data = subset(pf, !is.na(gender))) + 
  geom_boxplot() +
  stat_summary(fun.y = mean, geom = 'point', shape = 4)

library(dplyr)

pf.fc_by_age_gender <- pf %>%
    filter(!is.na(gender)) %>%
    group_by(age, gender) %>%
    summarise(mean_friend_count = mean(friend_count),
              median_friend_count = median(friend_count),
              n = n()) %>%
  ungroup() %>%
  arrange(age)

head(pf.fc_by_age_gender)

```

*** 

### Plotando gráfico de linha por age e friend_count


```{r}

ggplot(aes(x = age, y = friend_count), 
       data = subset(pf, !is.na(gender))) +
  geom_line(aes(color = gender), stat = 'summary', fun.y = median)
```


***

### Plotting Conditional Summaries
Notes:

```{r Plotting Conditional Summaries}



ggplot(aes(x = age, y = median_friend_count), 
       data = pf.fc_by_age_gender) +
  geom_line(aes(color = gender))

```

***

### Thinking in Ratios
Notes:

***

### Wide and Long Format
Notes:

***

```{r}
spread(subset(pf.fc_by_age_gender, select = c('gender', 'age', 'median_friend_count')), gender, median_friend_count)
```


### Reshaping Data
Notes:

```{r}
install.packages('reshape2')
library(reshape2)
library(tidyr)
#remodelagem usando dplyr e tidyr
pf.fc_by_age_gender.wide <- spread(subset(pf.fc_by_age_gender, select = c('gender', 'age', 'median_friend_count')), gender, median_friend_count)
#ou a opção abaixo que inclui a proporção de mulheres x homens
pf.fc_by_age_gender.wide <- subset(pf.fc_by_age_gender[c('age', 'gender', 'median_friend_count')], !is.na(gender)) %>% 
    spread(gender, median_friend_count) %>% 
    mutate(ratio = female / male) 

#remodelagem usando reshape
pf.fc_by_age_gender.wide <- dcast(pf.fc_by_age_gender,
                                  age ~ gender,
                                  value.var = 'median_friend_count')


```


***

### Ratio Plot
Notes: É possível notar que as mulheres mais jovens possuem a mediana 2,5x maior que a media dos homens da mesma idade.

```{r Ratio Plot}

ggplot(aes(x = age, y = ratio),
       data = pf.fc_by_age_gender.wide) +
  geom_line() +
  geom_hline(yintercept = 1, alpha = 0.3, linetype = 2)

```

***

### Third Quantitative Variable
Notes:A variável tenure armazena o número de dias desde que o usuário se cadastrou no facebook.
Obs: A função floor() serve para arrendodar para baixo do inteiro mais próximo. 
A função ceiling() serve para arredondar para cima do inteiro mais próximo.

```{r Third Quantitative Variable}

pf$year_joined <- floor(2014 - pf$tenure/365)

```

***

### Cut a Variable
Notes: Separa os dados em bloco:
        (2004, 2009]
        (2009, 2011]
        (2011, 2012]
        (2012, 2014]


```{r Cut a Variable}

pf$year_joined.bucket <- cut(pf$year_joined,
                          c(2004, 2009, 2011, 2012, 2014))

table(pf$year_joined.bucket, useNA = 'ifany')

```

***

### Plotting it All Together
Notes:

```{r Plotting it All Together}

ggplot(aes(x = age, y = friend_count), 
       data = subset(pf, !is.na(year_joined.bucket))) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary', fun.y = median)


```

***

### Plot the Grand Mean
Notes:Os usuários mais recentes estão abaixo da média geral

```{r Plot the Grand Mean}

ggplot(aes(x = age, y = friend_count), 
       data = subset(pf, !is.na(year_joined.bucket))) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary', fun.y = mean) +
  geom_line(stat = 'summary', fun.y = mean, linetype = 5)

```

***

### Friending Rate
Notes: Taxa de amizades por dia

```{r Friending Rate}

with(subset(pf, tenure >= 1), summary(friend_count / tenure))

```

***

### Friendships Initiated
Notes: 

Os usuários mais novos aceitam solicitações aleatoriamente? Ou os usuários com mais tempo de registro iniciam mais amizades ? 

What is the median friend rate? 

What is the maximum friend rate?

```{r Friendships Initiated}
ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)
```

***

### Bias-Variance Tradeoff Revisited
Notes:

```{r Bias-Variance Tradeoff Revisited}

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)

ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

```

***

### Sean's NFL Fan Sentiment Study
Notes:

***

### Introducing the Yogurt Data Set
Notes:

***

### Histograms Revisited
Notes:

```{r Histograms Revisited}

```

***

### Number of Purchases
Notes:

```{r Number of Purchases}

```

***

### Prices over Time
Notes:

```{r Prices over Time}

```

***

### Sampling Observations
Notes:

***

### Looking at Samples of Households

```{r Looking at Sample of Households}

```

***

### The Limits of Cross Sectional Data
Notes:

***

### Many Variables
Notes:

***

### Scatterplot Matrix
Notes:

***

### Even More Variables
Notes:

***

### Heat Maps
Notes:

```{r}
nci <- read.table("nci.tsv")
colnames(nci) <- c(1:64)
```

```{r}
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```


***

### Analyzing Three of More Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

